Verifying Demonstrations

### 2021-06-15 paper/intro.tex
Adds outline as titled paragraph in intro

The paper is organized as follows.
In \Cref{system-model}, we describe our system model and summarize the desired 
properties for crowd counting, followed by a discussion of current 
crowd-counting methods in \cref{current-crowd-counting}. In \Cref{definitions}, 
we formalize the notion of protest and the desired verifiability and privacy 
properties, and in \cref{building-blocks}, we give the relevant background on 
the building blocks of our solution.
%
%\Cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, 
%different from that originally proposed by \textcite{DistanceBounding}.
%We provide a proof of its security and formally verify it using 
%Tamarin~\cite{TamarinDB}.
%
We present \CROCUS, a privacy-preserving crowd counting 
%estimation 
protocol in in \cref{trusted-witnesses-protocol,untrusted-witnesses-protocol}, 
analyze its security in \cref{SecurityAnalysis}, and estimate its performance 
in \cref{PerformanceAnalysis}.
We compare it to related work in \cref{related-work}.
Finally, we discuss limitations and assumptions in \cref{Discussion} and give 
our conclusions in \cref{Conclusion}.

>>>>

\paragraph{Outline}

The paper is organized as follows.
In \Cref{system-model}, we describe our system model and summarize the desired 
properties for crowd counting, followed by a discussion of current 
crowd-counting methods in \cref{current-crowd-counting}. In \Cref{definitions}, 
we formalize the notion of protest and the desired verifiability and privacy 
properties, and in \cref{building-blocks}, we give the relevant background on 
the building blocks of our solution.
%
%\Cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, 
%different from that originally proposed by \textcite{DistanceBounding}.
%We provide a proof of its security and formally verify it using 
%Tamarin~\cite{TamarinDB}.
%
We present \CROCUS, a privacy-preserving crowd counting 
%estimation 
protocol in in \Cref{Protocol}, analyze its security in \cref{SecurityAnalysis}, and estimate its performance in \cref{PerformanceAnalysis}.
We compare it to related work in \cref{related-work}.
Finally, we discuss limitations and assumptions in \cref{Discussion} and give 
our conclusions in \cref{Conclusion}.
